Using Fundamental Measure Theory to Treat the Correlation Function of the Inhomogeneous Hard-Sphere Fluid

### 2012-08-21 papers/contact/paper.tex
switch A and S to $A$ and $S$ in contact paper Tested everything on node05.

The S case correlation functions do not match the monte carlo simulated correlation as well as the functionals of Yu and Wu.  For the walls and the sperical cavity, the monte carlo simulations show this function going to zero at these surfaces, roughly beginning its downward trend at about one sphere radius out.  This stands to reason since that because there is an increased density up against the wall, there is little chance that points within a radius of the wall and the center of those spheres will be a contact point between two spheres, since the hard spheres cannot overlap.

The A correlation White Bear calculations match up very well with monte-carlo simulation.  Although they seem to be both very close, the Gross functional deos not have the near perfect overlap with simulation that the White Bear calculation deos.

@@

We once again see that in the S case, although neither functionals tested fit perfectly, Yu and Wu's functional is a closer fit than the White Bear's.  We can see in the monte carlo's oscillations over increased distance from the surfaces that there are layers of spheres that are formed.  If one picks a point in one of these layters, that point is more likely to be a contact point between spheres, whereas if one picks a sphere a little over half a radius away, the likelyhood is at a minimum.  There is then another maximum at roughly one radius away from the surface.  (This suggests close packed layers?)

As with the lower densities, the A case White Bear fits to the monte carlo simulations very well.  The Gross functional seems to be accurate until it falls off close to surfaces.

@@

In our expressions for pressure (eq \ref{eq:p_{HS}^A} and eq
\ref{eq:p_{HS}^S}) we have $\frac{\delta A_{HS}}{\delta
  \sigma(\mathbf{r})}$ terms that must be derived for both the S and A
cases.  We break these terms up as follows:

@@

We must therefore compute both the $\frac{\delta A_{HS}}{\delta
  n(\mathbf{r}')}$, etc., terms and the $\frac{\delta
  n(\mathbf{r}')}{\delta \sigma(\mathbf{r})}$, etc., terms.  We will
compute the $\frac{\delta A_{HS}}{\delta n(\mathbf{r}')}$, etc., terms
for both the functional derived in the White Bear I formulation and
for that in the White Bear II formulation.  Following this we will
compute the $\frac{\delta n(\mathbf{r}')}{\delta \sigma(\mathbf{r})}$,
etc., terms for both the A and S cases.  These latter derivitives will
differ for the A and S cases according to the qualitive concepts
described above.

>>>>

The $S$ case correlation functions do not match the monte carlo
simulated correlation as well as the functionals of Yu and Wu.  For
the walls and the sperical cavity, the monte carlo simulations show
this function going to zero at these surfaces, roughly beginning its
downward trend at about one sphere radius out.  This stands to reason
since that because there is an increased density up against the wall,
there is little chance that points within a radius of the wall and the
center of those spheres will be a contact point between two spheres,
since the hard spheres cannot overlap.

The $A$ correlation White Bear calculations match up very well with
monte-carlo simulation.  Although they seem to be both very close, the
Gross functional deos not have the near perfect overlap with
simulation that the White Bear calculation deos.

@@

We once again see that in the $S$ case, although neither functionals
tested fit perfectly, Yu and Wu's functional is a closer fit than the
White Bear's.  We can see in the monte carlo's oscillations over
increased distance from the surfaces that there are layers of spheres
that are formed.  If one picks a point in one of these layers, that
point is more likely to be a contact point between spheres, whereas if
one picks a sphere a little over half a radius away, the likelyhood is
at a minimum.  There is then another maximum at roughly one radius
away from the surface.  (This suggests close packed layers?)

As with the lower densities, the $A$ case White Bear fits to the monte
carlo simulations very well.  The Gross functional seems to be
accurate until it falls off close to surfaces.

@@

In our expressions for pressure (eq \ref{eq:p_{HS}^A} and eq
\ref{eq:p_{HS}^S}) we have $\frac{\delta A_{HS}}{\delta
  \sigma(\mathbf{r})}$ terms that must be derived for both the $S$ and A
cases.  We break these terms up as follows:

@@

We must therefore compute both the $\frac{\delta A_{HS}}{\delta
  n(\mathbf{r}')}$, etc., terms and the $\frac{\delta
  n(\mathbf{r}')}{\delta \sigma(\mathbf{r})}$, etc., terms.  We will
compute the $\frac{\delta A_{HS}}{\delta n(\mathbf{r}')}$, etc., terms
for both the functional derived in the White Bear I formulation and
for that in the White Bear II formulation.  Following this we will
compute the $\frac{\delta n(\mathbf{r}')}{\delta \sigma(\mathbf{r})}$,
etc., terms for both the $A$ and $S$ cases.  These latter derivitives will
differ for the $A$ and $S$ cases according to the qualitive concepts
described above.
